Inefficient Concessions and Mediation

### 2021-01-12 notes.tex
add notes on other examples of inefficient concessions

\subsection{Destroying weapons}
I'm not sure this is perfect: it's a bit of a stretch to say the weapons could be given to the negotiating partner who could use them to build up civil society, but I guess if they're given to non-militarized police to enforce law and order...
\begin{itemize}
	\item FARC in 2017 (Colombia)
		\begin{itemize}
			\item https://www.crisisgroup.org/latin-america-caribbean/andes/colombia/statement-transitional-justice-agreement-between-colombian-government-and-farc
			\item https://news.un.org/en/story/2017/06/560442-colombia-un-mission-collects-nearly-all-remaining-weapons-farc-ep
			\item https://unmc.unmissions.org/en/un-mission-finalises-extraction-arms-caches-and-laying-down-weapons-farc-ep
		\end{itemize}
	\item Northern Ireland
		\begin{itemize}
			\item Report of the Independent International Commission on Decomissioning: https://cain.ulster.ac.uk/events/peace/decommission/iicd260905.pdf
			\item Note two years later: https://www.crisisgroup.org/crisiswatch/october-2007
			\item Summary: https://cain.ulster.ac.uk/events/peace/decommission.htm
		\end{itemize}
		\item Philippines / Bangsamoro region: https://www.crisisgroup.org/asia/south-east-asia/philippines/301-philippines-militancy-and-new-bangsamoro
	\item Yemen, \url{https://www.crisisgroup.org/crisiswatch/print?page=1&location%255B%255D=28&date_range=custom&from_month=01&from_year=2020&to_month=04&to_year=2020&t=CrisisWatch+Database+Filter}
		\begin{itemize}
			\item https://www.arabnews.com/node/1292091/middle-east
			\item As part of “Phase 2” agreement...Rival Yemeni groups 24 Jan completed transfer of heavy weapons in Aden to Saudi-controlled base in city within fifteen-day timeframe. After early redeployments from Aden, process again stalled late Jan, with local appointments still not made. 
		\end{itemize}
\end{itemize}

\subsection{Other conflicts to investigate}
\begin{itemize}	
	\item Liberia
	\item What happened to make peace in Sudan?
	\item Taliban in Afghanistan? February 29, 2020
		\begin{itemize}
			\item No help from International Crisis Group
		\end{itemize}
	\item Iran deal with the U.S.: JCPOA
	\item North and South Korea
\end{itemize}

>>>>

\subsection{Destroying weapons}
I'm not sure this is perfect: it's a bit of a stretch to say the weapons could be given to the negotiating partner who could use them to build up civil society, but I guess if they're given to non-militarized police to enforce law and order...
\begin{itemize}
	\item On disarmament in general: https://cain.ulster.ac.uk/events/peace/docs/disarmament.htm
	\item FARC in 2017 (Colombia)
		\begin{itemize}
			\item https://www.crisisgroup.org/latin-america-caribbean/andes/colombia/statement-transitional-justice-agreement-between-colombian-government-and-farc
			\item https://news.un.org/en/story/2017/06/560442-colombia-un-mission-collects-nearly-all-remaining-weapons-farc-ep
			\item https://unmc.unmissions.org/en/un-mission-finalises-extraction-arms-caches-and-laying-down-weapons-farc-ep
		\end{itemize}
	\item Northern Ireland
		\begin{itemize}
			\item Report of the Independent International Commission on Decomissioning: https://cain.ulster.ac.uk/events/peace/decommission/iicd260905.pdf
			\item Note two years later: https://www.crisisgroup.org/crisiswatch/october-2007
			\item Summary: https://cain.ulster.ac.uk/events/peace/decommission.htm
		\end{itemize}
		\item Philippines / Bangsamoro region: https://www.crisisgroup.org/asia/south-east-asia/philippines/301-philippines-militancy-and-new-bangsamoro
	\item Yemen, \url{https://www.crisisgroup.org/crisiswatch/print?page=1&location%255B%255D=28&date_range=custom&from_month=01&from_year=2020&to_month=04&to_year=2020&t=CrisisWatch+Database+Filter}
		\begin{itemize}
			\item https://www.arabnews.com/node/1292091/middle-east
			\item As part of “Phase 2” agreement...Rival Yemeni groups 24 Jan completed transfer of heavy weapons in Aden to Saudi-controlled base in city within fifteen-day timeframe. After early redeployments from Aden, process again stalled late Jan, with local appointments still not made. 
		\end{itemize}
	\item Liberia: https://peaceaccords.nd.edu/accord/accra-peace-agreement, https://www.un.org/press/en/1999/19990726.SGSM7078.html
\end{itemize}

\subsection{Other conflicts}
I investigated these for different types of inefficiencies but did not find anything useful
\begin{itemize}	
	\item North and South Korea
	\item What happened to make peace in Sudan?
	\item Liberia--don't see anything in the Accra accords
	\item Taliban in Afghanistan? February 29, 2020
		\begin{itemize}
			\item No help from International Crisis Group
			\item Read agreement on state.gov; it's only four pages long, not much too it
		\end{itemize}
	\item Iran deal with the U.S.: JCPOA
\end{itemize}
